### 2021-06-17 manuscript/conclusions.tex
Correcoes da Valeria pro relatorio finalizada.

In this work, we were able to develop a fast equivalent layer technique for processing magnetic data with the method of Conjugate Gradient Least Square using the convolutional equivalent layer theory presented in \cite{siqueira-etal2017} to obtain similar results. The sensitivity matrix of the magnetic equivalent layer carries the structure of BTTB matrices, which means a very low computational cost matrix-vector product and also the possibility to store only the first column of the matrix BCCB. In this work we propose a method to calculate the first six columns of the second derivatives matrices to embbed them into BCCB and then finally arrive in what would be the first column of the BCCB matrix embbeded from the sensitivity matrix.

>>>>

In this work, we were able to develop a fast equivalent layer technique for processing magnetic data with the method of Conjugate Gradient Least Square using the convolutional equivalent layer theory to obtain results of performance more than four orders of magnitude less than the classical equivalent layer. The sensitivity matrix of the magnetic equivalent layer carries the structure of BTTB matrices, which means a very low computational cost matrix-vector product and also the possibility to store only the first column of the matrix BCCB. In this work we propose a method to calculate the first six columns of the second derivatives matrices to embbed them into BCCB and then finally arrive in what would be the first column of the BCCB matrix embbeded from the sensitivity matrix.

### 2021-06-17 manuscript/field_data.tex
Correcoes da Valeria pro relatorio finalizada.

As this area is very large different values of the magnetic main field can be considered. 
For this test it was considered an approximated mid location of the area (latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ for the IGRF model in 01/01/2014. The inclination was calculated considering the Geocentric axial dipole model ($tang \, I = 2 \times tan \, \lambda$) and is equal to $12.84^{\circ}$.
As the source magnetization is unknown, inclination and declination equals to the main field is being used.

Figure \ref{fig:carajas_real_data_mag} shows the observed magnetic field data of the area. Using a equivalent layer at $300$ meters above the ground the predicted data and its residual are shown in figure \ref{fig:carajas_gz_predito_mag}. The mean of $-2.7135\times 10^{-07}$ nT and the standart deviation of $3.2726\times 10^{-06}$ nT of the residual shows the good result of physical property estimative. It was used 50 iterations of the CGLS method taking $15.5$ seconds with a Intel core i7 7700HQ@2.8GHz processor.

>>>>

As this area is very large different values of the magnetic main field can be considered. 
For this test it was considered an approximated mid location of the area (latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ for the IGRF model in 1st january, 2014. The inclination was calculated considering the Geocentric axial dipole model ($tang \, I = 2 \times tan \, \lambda$) and is equal to $12.84^{\circ}$. As the source magnetization is unknown, inclination and declination equals to the main field is being used.

Figure \ref{fig:carajas_real_data_mag} shows the observed magnetic field data of the area. Using a equivalent layer at $300$ meters above the ground the predicted data and its residual are shown in figure \ref{fig:carajas_gz_predito_mag}. The mean of $2.4566\times 10^{-06}$ nT and the standart deviation of $1.9787\times 10^{-06}$ nT of the residual shows the good result of physical property estimative. It was used 50 iterations of the CGLS method taking $15.5$ seconds with a Intel core i7 7700HQ@2.8GHz processor.

The convergence analysis is shown in figure \ref{fig:convergence_carajas_mag_500x500}
